---
title: "Homework1"
author: "Zhipeng Chen"
date: "9/23/2021"
output: html_document
---

## 1
### a

```{r}
a <- 0.7
b <- 0.2
c <- 0.1
```

$0.7_{10}$=$0.10110011001_{2}$  
$0.2_{10}$=$0.00110011001_{2}$  
$0.1_{10}$=$0.00011001100_{2}$  

### b, c, d
```{r}
(a + b) + c == 1
a + (b + c) == 1
(a + c) + b == 1
```
### e
The question b is false and the other two are both true. This may be caused by the rounding error. The real number cannot be exactly represented by floating-point computation. For example, the decimal number 0.1 has a finite decimal representation, in binary it has an infinite repeating representation.

## 2
### a
```{r}
x <- 0.001 * (988:1012)
y1 <- x^7 - 7*x^6 + 21*x^5 - 35*x^4 + 35*x^3 - 21*x^2 + 7*x - 1
plot(x, y1)
```
### b
```{r}
y2 <- (x - 1)^7
plot(x, y2)
```
### c
The plot a is more precise than plot b. This may be caused by rounding error in floating-point computation.

## 3
### a
```{r}
u <- matrix(c(1, 2, 3, 3, 2, 1), 6, 1)
ut <- t(u)
d <- ut %*% u
part2 <- (2/as.vector(d)) * (u %*% ut)
U <- diag(6) - part2
U
```
### b
```{r}
C <- U %*% U
largest_off_diag <- max(C[lower.tri(C) | upper.tri(C)])
largest_off_diag
smallest_off_diag <- min(C[lower.tri(C) | upper.tri(C)])
smallest_off_diag
```
### c
```{r}
largest_diag <- max(diag(C))
largest_diag
smallest_diag <- min(diag(C))
smallest_diag
```
### d
```{r}
U %*% u
```
### e
```{r}
s <- max(rowSums(abs(U)))
s
```
### f
```{r}
print(U[3,])
```
### g
```{r}
print(U[3,2])
```
### h
```{r}
A <- U[,1:3]
P <- A %*% t(A)
P
```
### i
```{r}
max(rowSums(abs(((P %*% P) - P))))
library(matrixcalc)
is.idempotent.matrix(P)
```
The result is not zero. P is not idempotent. However, when I use the package "matrixcalc" to verify my answer, the result shows that P is a idempotent matrix.  

### j
```{r}
B <- U[,(ncol(U)-2):ncol(U)]
Q <- B %*% t(B)
Q
```
### k
```{r}
max(rowSums(abs(((Q %*% Q) - Q))))
is.idempotent.matrix(Q)
```
The result is not zero. Q is not idempotent. However, when I use the package "matrixcalc" to verify my answer, the result shows that Q is a idempotent matrix.  

### l
```{r}
P + Q
```

## 4
```{r}
oringp <- read.table("E:\\OneDrive\\Study\\PhD of Biostatistics\\4-Data Analysis\\HW1\\oringp.dat")
oringp <- oringp[complete.cases(oringp),]
cor(oringp$V4, oringp$V5)
```

## 5
### a
 - All R functions have three parts:

    - the `formals()`, the list of **arguments** which controls how you can call the function
 
    - the `body()`, the **code** inside the function
    
    - the `environment()`, the "map" of the location of the function's variables

### b
```{r}
x <- 10
f1 <- function(x){
    function(){
        x + 10
    }
}
f1(1)()
```
### c
```{r}
mean(x = c(1:10, NA), na.rm = TRUE)
```
### d
```{r}
f2 <- function(a, b){
  return(a * 10)
}
f2(10, stop("This is an error!"))
```
There is no error when called since we don't use b when call the function.

## 6
### a
```{r}
matrixA <- function(n){
  stA <- matrix(0, nrow = n, ncol = n)
  for (i in 1:n){
    for (j in 1:n){
      stA[i, j] = 1 / (abs(i - j) + 1)
    }
  }
  stA
}
```

### b
```{r}
matrixA(10)
```
### c
```{r}
chol(matrixA(10))
```
### d
```{r}
det(matrixA(10))
```