---
title: "Lab4_ggplot2"
author: "Zhipeng Chen"
output: pdf_document
---

```{r}
rm(list = ls()) # clean-up workspace
library("tidyverse")
```

## Some exercise on ggplot2

### Aesthetic mappings

Q1. What's gone wrong with this code?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```
The bracket should be placed after "y = hwy,".


Q2. Which variables in `mpg` are categorical? Which variables are continuous?
(Hint: type `?mpg` to read the documentation for the dataset).
How can you see this information when you run `mpg`?
```{r}
summary(mpg)
```

Q3. Map a continuous variable to `color`, `size`, and `shape`.
How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = cyl))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, size = cyl))
#ggplot(data = mpg) +
#  geom_point(mapping = aes(x = displ, y = hwy, shape = cyl))
```
A continuous variable can not be mapped to shape.

Q4. What happens if you map the same variable to multiple aesthetics?
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = class, size = class, shape = class))
```
The class will be different by all of them.


Q5. What happens if you map an aesthetic to something other than a variable name, like `aes(colour = displ < 5)`? Note, you’ll also need to specify `x` and `y`.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = cyl > 5))
```
There are different color shown up that differs from "True" or "False" by the condition.


### Geometric objects

Q6. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?  
1. geom_smooth 2. geom_boxplot 3. geom_bar 3. geom_polygon

Q7. Will these two graphs look different? Why/why not?

```{r, eval=FALSE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```
They are the same.
