---
title: "Lab2"
author: "Zhipeng Chen"
output:
  html_document: default
---


## More on types
```{r}
a <- c(1L, "This is a character")
b <- c(TRUE, "Hello World")
c <- c(FALSE, 2) #what is wrong here
```
### Question 1 What type do the vectors hold?
a: Character. Since the integer 1 has been coerced to the highest type which is character.

b: Character. Since the logical object has been coerced to the highest type which is character.

c: numeric. Since 0 is considered to be false. Also the logical object has been coerced to the highest type which is numeric.

## Explicit coercion
```{r}
# using the same objects a, b, c from the above question
a.logical <- as.logical(a)
a.integer <- as.integer(a)
a.numeric <- as.numeric(a)
```
```{r}
b.logical <- as.logical(b)
b.integer <- as.integer(b)
b.numeric <- as.numeric(b)
```
```{r}
c.logical <- as.logical(c)
c.integer <- as.integer(c)
c.numeric <- as.numeric(c)
c.character <- as.character(c)

d <- -5:5
d.logical <- as.logical(d)
```
### Question 2 What do you get after the coercions? Does any one suprise you? Can you figure out why?
The c.logical and d.logical suprise me. Since in R, the zero is false and non-zero is ture.

## Try arithmetics
```{r}
v <- c(969,971:1023)
```

```{r}
v.power.sum <- sum(2^v)
```

```{r}
v.power.sum.53 <- sum(2^v[-1])
```

```{r}
v.power.sum.second <- 2^v[1] + sum(2^v[-1])
```
### Question 3 Explain what you found
If we do the sum directly, the result is infinity since the result is divergence after adding separately.


